---
title: "GRAPHS-2015 Exploratory Data Analysis"
nocite: |
  @kotthoff_portfolios_2016
output:
  html_document:
    df_print: paged
    toc: yes
  html_notebook:
    theme: united
    toc: yes
bibliography: GRAPHS-2015/citation.bib
---

## Description

Displays summary statistics and plots on the [GRAPHS-2015](https://github.com/coseal/aslib_data/tree/master/GRAPHS-2015) dataset. All statistics and plotting functions used are from the [ASlib](https://www.rdocumentation.org/packages/aslib/versions/0.1) package.

```{r load_dataset}
library(aslib)
dataset = parseASScenario("GRAPHS-2015")
summary(dataset)
```

## Summary of features 
```{r}
getFeatureNames(dataset)
summarizeFeatureValues(dataset)
```

## Summary of algorithm performance
```{r}
getAlgorithmNames(dataset)
summarizeAlgoPerf(dataset) 
```

```{r}
summarizeAlgoRunstatus(dataset)
```


## Algorithm performance plots
Important note w.r.t.\ some of the following plots:
If appropriate, we imputed performance values for failed runs.
We used $max + 0.3 * (max - min)$, in case of minimization problems,
or $min - 0.3 * (max - min)$, in case of maximization problems.

```{r}
plotAlgoPerfBoxplots(dataset, impute.zero.vals = TRUE, log = TRUE)
```
```{r}
plotAlgoPerfDensities(dataset, impute.zero.vals = TRUE, log = TRUE)
```
```{r}
plotAlgoPerfCDFs(dataset, impute.zero.vals = TRUE, log = TRUE)
```
```{r}
plotAlgoPerfScatterMatrix(dataset, impute.zero.vals = TRUE, log = TRUE)
```

### Correlation matrix
The figure showing the correlations of the ranks of the performance values shows
the Spearman correlation coefficient. Missing values were imputed prior to
computing the correlation coefficients. The algorithms are ordered in a way that
similar (highly correlated) algorithms are close to each other. Per default the
clustering is based on hierarchical clustering, using Ward's method.
```{r}
plotAlgoCorMatrix(dataset)
```

## References
[Source Rmd file](https://github.com/kvrigor/algosel-rl/blob/master/ntbk_eda_graphs2015.Rmd)

[GRAPHS-2015 EDA original source](https://github.com/ciaranm/lion2016-sip-portfolios-paper/blob/master/portfolio/as-graphs.Rnw)
